---
title: "fMRI Prereg V2.0"
date: "2020/07/28"
toc: true
output:
  pdf_document: default
  html_document: default
  word_document: default
---

<!-- 

**[Discussion points]**

- [detailed vs. concise description of elements, or support both?]
- [template might be too overwhelming if detailed -\> rather break down by using 
    mandatory/optional, maybe have "defaults" of programs in supplements/methods part to make sure they are reported]
- [lots of details about things that you cannot change after you have conducted your experiment (fmri sequence), 
    most people preregister after they have acquired their task]
- [move acquisition parameters and other parts which are important for manuscript but not for preregistration to appendix]
- [mark recommended and essential labels (e.g., relating to the choice of going with a detailed vs. concise description)]
- [other modalities (to be added after publishing the fMRI specific template)]
- [incorporate fmriprep's defaults]
- [align structure with structure of a manuscript: decision: keep current order (OSF template) and move into a more concise version]
- [use tables as list of check boxes when writing methods section]
- [power analysis: unknown effect sizes and practical limitations in fMRI studies rather than a-priori power analysis which are rarely done. 
   Exploratory vs. confirmatory analyses,] 
   
-->

# Usage Notes to the template

_The goal of this template is to provide sufficient information in
preregistration of fMRI studies to increase reproducibility._

_A \* indicates you should fill out this section, all other sections are
optional._

*You can use the tables to fill in your design specifications, or use them as
checklists of information you include in the text for in attached files (e.g.,
json file of scan parameters). If a certain table/section does not apply, just
state "NA." Tip: Using it as a checklist will allow you to write these sections
as they will appear in your future paper.*


```{r child='01_study_information.Rmd'}
```

```{r child='02_design_plan.Rmd'}
```

```{r child='03_sampling_plan.Rmd'}
```

```{r child='04_variables.Rmd'}
```

```{r child='05_analysis_plan.Rmd'}
```

```{r child='appendix_1.Rmd'}
```

```{r child='appendix_2.Rmd'}
```

```{r child='appendix_3.Rmd'}
```

